---
title: YOUR TITLE
author: YOUR NAME
date: Month date, YEAR
output: 
  revealjs::revealjs_presentation:
    pandoc_args: [ "--slide-level", "2" ]
    self_contained: false
    reveal_plugins: ["menu","notes"]
    reveal_options:
      slideNumber: true
      menu:
        numbers: true
    transition: "fade"
    theme: night
    highlight: pygments
    css: styles.css
    center: true
---

# Two columns 1 {data-background="fig/IPB_logo.svg" data-background-size="120px" data-background-position="top 25px left 50px"}

<style>
.column-left{
  float: left;
  width: 48%;
  text-align: left;
}
.column-right{
  float: right;
  width: 48%;
  text-align: left;
}
</style>

<div class="column-left">
```{r, echo=FALSE, warning=FALSE, fig.height=5, fig.width=5}
library(leaflet)
m <- leaflet() %>%
  addTiles() %>%
  addMarkers(lat=-6.55717599, lng=106.72295884, popup="Zoo Corner")
m
```
ZooCorner
</div>

<div class="column-right">  
```{r, echo=FALSE, warning=FALSE, fig.height=5, fig.width=5}
library(leaflet)
m <- leaflet() %>%
  addTiles() %>%
  addMarkers(lat=-6.55717599, lng=106.72295884, popup="Zoo Corner")
m
```
</div>

# Two columns 2 {data-background="fig/IPB_logo.svg" data-background-size="120px" data-background-position="top 25px left 50px"}

<style>
.container{
  display: flex;
}
.col{
  flex: 1;
}
</style>

<div class="container">
<div class="col">
```{r, echo=FALSE, warning=FALSE, fig.height=5, fig.width=5}
library(leaflet)
m <- leaflet() %>%
  addTiles() %>%
  addMarkers(lat=-6.55717599, lng=106.72295884, popup="Zoo Corner")
m
```
</div>
<div class="col">
```{r, echo=FALSE, warning=FALSE, fig.height=5, fig.width=5}
library(leaflet)
m <- leaflet() %>%
  addTiles() %>%
  addMarkers(lat=-6.55717599, lng=106.72295884, popup="Zoo Corner")
m
```
</div>
</div>

# Two columns 3

<style>
.twocolumn {
   display: grid;
   grid-template-columns: 1fr 1fr;
   grid-gap: 10px;
   text-align: left;
}
</style>

<div class="twocolumn">
  <div>
```{r, echo=FALSE, warning=FALSE, fig.height=5, fig.width=5}
library(leaflet)
m <- leaflet() %>%
  addTiles() %>%
  addMarkers(lat=-6.55717599, lng=106.72295884, popup="Zoo Corner")
m
```
  </div>
  <div>
```{r, echo=FALSE, warning=FALSE, fig.height=5, fig.width=5}
library(leaflet)
m <- leaflet() %>%
  addTiles() %>%
  addMarkers(lat=-6.55717599, lng=106.72295884, popup="Zoo Corner")
m
```
  </div>
</div>


# You have a menu..
..click the three-horizontal-bar on the bottom-left..

# You can have notes..
..try click »S« key to open the *notes* window..  

<div class="notes">
..but notes plugin inhibit you to do self_contained: true

- It can contain markdown
- like this list
</div>
